---
title: "Cabbages"
author: "Andrew Valles Tovar"
date: "2/2/23"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(VitC~Cult,data=veggy)
```

According to the box plot, C52 contains more vitamin C than C39. We are able to determine this by seeing that the C52 box on the box plot is placed higher than the C39 box.
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```

The mean of C52, 64.4, is substantially higher than C39. Also, C52 prevails in other categories such as Q1, median, Q3, and others as well. C39 does not go above any category than C52 in this data.
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(VitC~Cult,data=veggy)
```

The chances that this could happen if there really is no difference between C39 and C52 cultivation methods is 0.00000003405%. The chances of this happening are extremely slim. Therefore, I believe the hypothesis doesn't hold value on there being no difference.
  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
In summary, the cultivation method for C52 contains more vitamin C than the cultivation method for C39. The box plot, numerical descriptive results, and the inferential results clearly shows that the cultivation method for C52 is more beneficial than C39. The hypothesis from the inferential data states that there is no difference between the cultivation methods of C39 and C52, but only at a 0.00000003405% chance of being true. C52 cultivation methods reign supreme in all categories than C39 could ever do.